# RMarkdown

Here are 5 exercises and their solutions that test a user's understanding of R Markdown:

### Exercise 1: Basic Markdown Formatting

Create an R Markdown document with the following text elements:

1. A level-1 header named "Introduction".
2. A paragraph of text.
3. A level-2 header named "Formatting".
4. A bulleted list with three items.
5. A numbered list with three items.

**Solution:**

```markdown
# Introduction

This is a simple paragraph of text.

## Formatting

- Item 1
- Item 2
- Item 3

1. Item 1
2. Item 2
3. Item 3
```

### Exercise 2: Text Formatting

Write an R Markdown document that includes the following:

1. Bold text.
2. Italic text.
3. A blockquote.

**Solution:**

```markdown
**This is bold text.**

*This is italic text.*

> This is a blockquote.
```

### Exercise 3: Insert an R Code Chunk

Create an R Markdown document with an R code chunk that calculates the mean of the numbers 1 to 10.

**Solution:**

```markdown
```{r}
mean(1:10)
```
```

### Exercise 4: Display a Table

Create an R Markdown document that displays the first 5 rows of the `mtcars` dataset as a table.

**Solution:**

```markdown
```{r}
library(knitr)
kable(head(mtcars, n = 5), caption = "First 5 rows of the mtcars dataset")
```
```

### Exercise 5: Create a Plot

Create an R Markdown document that generates a bar plot of the number of cylinders in the `mtcars` dataset using `ggplot2`.

**Solution:**

```markdown
```{r}
library(ggplot2)

ggplot(mtcars, aes(x = factor(cyl))) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Number of Cars by Cylinders",
       x = "Number of Cylinders",
       y = "Count")
```
```

These exercises cover various aspects of R Markdown, including formatting, embedding R code chunks, and generating tables and plots. Completing these exercises will help users become more familiar with R Markdown's capabilities.