---
title: "R Markdown Demo"
author: "R. Burke Squires"
date: "2023-04-27"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# Introduction

This is a simple demonstration of R Markdown's capabilities. R Markdown allows you to write text using Markdown syntax, embed R code, and produce dynamic output in various formats.

# Markdown Formatting

## Headers

You can create headers using the `#` symbol:

# H1
## H2
### H3

## Text Formatting

You can create *italic text* using a single asterisk or underscore:

*Italic text* or _Italic text_

You can create **bold text** using double asterisks or underscores:

**Bold text** or __Bold text__

## Lists

You can create unordered lists using asterisks, plus signs, or hyphens:

* Item 1
* Item 2

You can create ordered lists using numbers followed by periods:

1. Item 1
2. Item 2

# R Code Chunks

You can embed R code chunks using three backticks followed by `{r}`:

```{r}
# Here's an example R code chunk
library(ggplot2)
data(mtcars)
head(mtcars)
```

# Plotting

You can also include plots in your R Markdown document. Here's a scatter plot using the `mtcars` dataset:

```{r}
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Scatter plot of MPG vs Weight",
       x = "Miles per Gallon",
       y = "Weight (1000 lbs)")
```

# Tables

You can create tables using the `knitr::kable()` function:

```{r}
library(knitr)
kable(head(mtcars), caption = "First 6 rows of the mtcars dataset")
```

# Conclusion

R Markdown is a powerful tool for creating dynamic documents that combine text, code, and output. It allows for easy sharing of analysis and results with others in a wide range of formats.
```

Save this file with the `.Rmd` extension and use the `rmarkdown::render()` function in R to generate an output document.