---
title: "R Notebook - Mock Analysis"
author: "Ann Alyzer"
output:
  html_document:
    df_print: paged
---

# Gapminder Analysis

- The [Gapminder project](https://www.gapminder.org/data/) has collected data from countries around the world that look at communication, economic, education, environment, health, infrastructure, population, society, and work in each country since the 1950s.

In this particular analysis we will be looking at the trends over time of life expectancy versus a country's gross domestic product or GDP. Gross domestic product (GDP) is the standard measure of the value added created through the production of goods and services in a country during a certain period. As such, it also measures the income earned from that production, or the total amount spent on final goods and services (less imports)[1].

## Analysis Plan

1. Import data
1. Analyze data
1. Plot data
1. Draw amazing conclusions!

## Import libraries and data

```{r}
library("ggplot2")
source("../bin/chunk-options.R")
knitr_fig_path("01-")
# Silently load in the data so the rest of the lesson works
gapminder <- read.csv("../data/gapminder_data.csv", header = TRUE)
```

## Preview the Gapminder data

```{r}
print(gapminder)
```


```{r lifeExp-line-point}
ggplot(data = gapminder, mapping = aes(x=year, y=lifeExp, by=country, color=continent)) +
  geom_line() + geom_point()
```


```{r lm-fit2}
ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp)) +
  geom_point(alpha = 0.5) + scale_x_log10() + geom_smooth(method="lm", size=1.5)
```


---

[1] https://data.oecd.org/gdp/gross-domestic-product-gdp.htm