---
title: "Data Analysis Workflow with Iris Dataset"
author: "R. Burke Squires"
date: "2023-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(caret)
```

# Introduction

This R Markdown document demonstrates a data analysis workflow using the `iris` dataset. We'll explore the dataset, visualize the data, and create a simple classification model.

# Data Exploration

First, let's take a look at the `iris` dataset.

```{r}
head(iris)
summary(iris)
```

The `iris` dataset contains 150 observations of iris flowers, with four measurements (sepal length, sepal width, petal length, and petal width) and the species of the iris.

# Data Visualization

Now, let's visualize the relationships between the variables using scatter plots.

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Sepal Length vs Sepal Width",
       x = "Sepal Length (cm)",
       y = "Sepal Width (cm)")

ggplot(iris, aes(x = Petal.Length, y = Petal.Width, color = Species)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Petal Length vs Petal Width",
       x = "Petal Length (cm)",
       y = "Petal Width (cm)")
```

The scatter plots suggest that the species are somewhat separable based on petal and sepal measurements.

# Model Creation

We'll create a simple classification model using the k-Nearest Neighbors (k-NN) algorithm. First, we'll split the dataset into training and testing sets.

```{r}
set.seed(42)
train_index <- createDataPartition(iris$Species, p = 0.8, list = FALSE)
train_data <- iris[train_index, ]
test_data <- iris[-train_index, ]
```

Now, let's train the k-NN model.

```{r}
model <- train(Species ~ ., data = train_data, method = "knn", trControl = trainControl(method = "cv", number = 10))
model
```

Finally, we'll evaluate the model's performance on the test dataset.

```{r}
predictions <- predict(model, test_data)
confusionMatrix(predictions, test_data$Species)
```

The k-NN model achieves a high accuracy on the test dataset, indicating that it's able to classify the iris species reasonably well based on the four measurements provided.

# Conclusion

In this R Markdown document, we've demonstrated a data analysis workflow using the `iris` dataset. Through data exploration, visualization, and model creation, we've shown that the iris species can be classified using their petal and sepal measurements.