---
title: "Dashboard Demo"
author: "R. Burke Squires"
date: "June 2025"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

To create a dashboard in R Markdown, we'll use the `flexdashboard` package. First, install and load the `flexdashboard` package, if you haven't already:

```R
install.packages("flexdashboard")
```

Now, create a new R Markdown file with the following content, which demonstrates the dashboard capability using `flexdashboard`:


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(shiny)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Scatter plot of MPG vs Weight

```{r}
renderPlot({
  ggplot(mtcars, aes(x = mpg, y = wt)) +
    geom_point() +
    theme_minimal() +
    labs(title = "Scatter plot of MPG vs Weight",
         x = "Miles per Gallon",
         y = "Weight (1000 lbs)")
})
```

Column {data-width=350}
-----------------------------------------------------------------------

### Controls

```{r}
sliderInput("mpg", "Miles per Gallon:",
            min = min(mtcars$mpg),
            max = max(mtcars$mpg),
            value = c(min(mtcars$mpg), max(mtcars$mpg)))

sliderInput("wt", "Weight (1000 lbs):",
            min = min(mtcars$wt),
            max = max(mtcars$wt),
            value = c(min(mtcars$wt), max(mtcars$wt)))
```

### Table

```{r}
renderTable({
  filtered_data <- mtcars[(mtcars$mpg >= input$mpg[1]) &
                            (mtcars$mpg <= input$mpg[2]) &
                            (mtcars$wt >= input$wt[1]) &
                            (mtcars$wt <= input$wt[2]), ]
  head(filtered_data)
})
```

Save this file with the `.Rmd` extension, and then you can use the `rmarkdown::render()` function in R to generate an interactive dashboard. This example dashboard features a scatter plot, a table, and sliders to filter the data.